Growing libraries of concepts with wake-sleep program induction

### 2018-07-30 nips_2018_author_response.tex
Figure, include R2 in the reponse

@@

\paragraph*{Example of evolution for a task through \texttt{DSL}s}

Find some logs and give an example I guess? I have a few available for geometry
but hey :/

@@

The \textsc{Igor} systems introduced by Kitzelmann and Schmid is a sophisticated
algorithm for analytical inductive programming that handles a certain classe of
programs, much like {Sketch} and {FlashFill} are sophisticated
program synthesiser for certain classes of programs.

>>>>

\usepackage[rightcaption]{sidecap}
\usepackage{graphicx}

@@

\begin{SCfigure}[2][h]
  \centering
  \includegraphics[width=7cm]{figures/rebutal/spirals.eps}\label{geomCompiled}
  \caption{Practical example of DSL evolution: originally, the preferred program
  for the leftmost spiral does not use loops while that of the two other does.
  After an iteration the structure of the two rightmost spiral is abstracted.
  For the next iteration the preferred program for the leftmost spiral leverages
  on that and changes in a meaningful way.}
\end{SCfigure}

@@

The \textsc{Igor} systems introduced by Kitzelmann and Schmid is a sophisticated
algorithm for analytical inductive programming that handles a certain classe of
programs, much like {Sketch} and {FlashFill} are sophisticated program
synthesiser for certain classes of programs. This also relates to an insightful
and suggestion for comparison by reviewer 2: FlashFill's DSL is fixed and
manually curated and enhanced for a specific class of problems, over which is
performs well at the loss of agility.
